### 2021-06-05 paper/report.tex
Add some references. Address some of HM's comments. Not running through. Probably missing curly bracket somewhere.

At the core of our agent-based model are physical contacts between heterogeneous agents (Figure~\ref{fig:broad_model_description}).\footnote{We provide a detailed comparison to other approaches in \ref{sec:literature_review}. The model most closely related to ours is described in \citet{Hinch2020}.} Each contact between an infectious indvidual and somebody susceptible to the disease bears the risk of transmitting the virus. Contacts occur in the household, at work, at school, or in other settings (leisure activities, grocery shopping, medical appointments, etc.).\comment[id=HM]{Systemic relevance of work?} Some contacts recur regularly, others occur at random. Random contacts are typically assortative in age and geographical location. Empirical applications can take the population structure from census data and the types and frequency of contacts from diary data measuring contacts before the pandemic \citep[e.g.][]{Mossong2008}.\comment[id=HM]{cite other stuff, too?} The dimensions are chosen so that the most common NPIs can be modelled in great detail by reducing the number of contacts in a particular setting or the risk of transmitting the disease for a type of contact. For example, a mandate to work from home will reduce the number of work contacts to zero for a fraction of the working population. Schools and daycare can be closed entirely, operate at reduced capacity including an alternating schedule, or implement mitigation measures like masking requirements or air filters.\comment[id=HM]{cite \url{https://science.sciencemag.org/content/early/2021/04/28/science.abh2939}} Curfews may reduce the number of contacts in non-work/non-school settings. In any setting, measures like masking requirements would reduce the probability of infection associated with a contact.

@@

Susceptibility to contracting the SARS-CoV-2 virus is dependent on age; so is the progression of a possible infection. We differentiate between an inital period of infection without being infectious or showing symptoms, being infectious (presymptomatic or asymptomatic), showing symptoms, requiring intensive care, and recovery or death. The probabilities of transitioning between these states depend on age; their duration is random within intervals calibrated to medical literature.\comment[id=HM]{Cite}. Conditional on the type of contact, infectiousness independent of ages.\comment[id=HM]{Cite current Drosten paper}

The model includes several other features, which are crucial to describe the evolution of the pandemic in 2020-2021. New virus strains with different profiles regarding infectiousness and disease progress can be introduced. With a probability calibrated to XXX\comment[id=HM]{Klara, please add citatiion}, vaccinated agents become immune and they do not transmit the virus. While vaccines are rolled out, priority may depend on age and occupation. Agents may demand two types of tests as described in Figure~\ref{fig:pcr_antigen_tests}. First, polymerase chain reaction (PCR) tests directly reveal whether an individual is infected or not. PCR tests require some time to be processed and there are always aggregate capacity constraints. Second, rapid antigen tests yield immediate results. Specificity and sensitivity of these tests is set according to the XXX data.\comment[id=HM]{subsequent PCR tests, quarantine, work/school}. Demand for rapid tests will depend on policy, e.g., prices, testing requirements before work, attending school, or visiting restaurants and shops.

Modelling a population of agents according to actual demographic characterists means that we can use a wide array of data to identify and estimate the model's many parameters.\footnote{See section S.X of the supplementary materials for an overview.}\comment[id=HM]{Need to make a list including symbols, maybe you can fetch the parameters from the model and then we brainstorm re notation?} Mobility data is used to model the reductions in work contacts. School and daycare policies are incorporated directly from official directives. Infection rates by age and geographical region are estimated to match to officially recorded numbers; so is the prevalence of virus strains. In order to translate simulated cases in our model to officially recorded cases, we use the model depicted in Figure~\ref{fig:model_for_official_cases}. \comment[id=HM]{Add a sentence.} A further advantage is that the simulated data have a structure that resembles datasets used for regression models, which allows additional plausibility checks by re-running the same models on the model-generated data.\comment[id=HM]{Only keep if we actually do something like that.}

@@

We apply this model to Germany. In March and April 2020, the country broke the first wave of the pandemic fairly quickly. Between mid-May and mid-September, daily new infections were below 20 per Million and day.\comment[id=HM]{Cite our world in data} We model the period mid-September 2020 to the end of May 2020. We pick the starting date for two reasons. First, we do not include the first wave because the environment was very different (e.g., aggregate PCR test capacity was much lower and we would require a very different model for calculating the share of known cases) and some data was not recorded yet.\comment[id=HM]{True?}. Second, a large fraction cases during summer of 2020 were traced to international travel,\comment[id=HM]{citation?}, but the precise number is difficult to model.

@@

        \includegraphics[width=\textwidth]{../figures/results/figures/data/testing/share_of_educ_participants_with_rapid_test}

        \includegraphics[width=\textwidth]{../figures/results/figures/data/testing/share_of_workers_with_rapid_test_offer_at_work}
        % fraction of workers must be multiplied with 0.6 because only that many actually
        % accept the offer

        \includegraphics[width=\textwidth]{../figures/results/figures/data/share_of_individuals_with_first_vaccine}

        Number of PCR tests

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_new_known_case_cropped}
        \caption{{\small Effects of different schooling scenarios after Easter}}
        \label{fig:schooling_scenarios_easter}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_newly_infected_cropped}
        \caption{{\small TBD}}
        \label{fig:to_be_determined}
    \end{subfigure}
    \vskip3ex

>>>>

At the core of our agent-based model are physical contacts between heterogeneous agents
(Figure~\ref{fig:broad_model_description}).\footnote{We provide a detailed comparison to
other approaches in \ref{sec:literature_review}. The model most closely related to ours
is described in \citet{Hinch2020}.} Each contact between an infectious indvidual and
somebody susceptible to the disease bears the risk of transmitting the virus. Contacts
occur in the household, at work, at school, or in other settings (leisure activities,
grocery shopping, medical appointments, etc.).\comment[id=HM]{Systemic relevance of
work?} Some contacts take place regularly, others occur at random. Random contacts are
typically assortative in age and geographical location. Empirical applications can take
the population structure from census data and the types and frequency of contacts from
diary data measuring contacts before the pandemic
\citep[e.g.][]{Mossong2008}.\comment[id=HM]{cite other stuff, too?} The dimensions are
chosen so that the most common NPIs can be modeled in great detail by reducing the
number of contacts in a particular setting or the risk of transmitting the disease for a
type of contact. For example, a mandate to work from home will reduce the number of work
contacts to zero for a fraction of the working population. Schools and daycare can be
closed entirely, operate at reduced capacity including an alternating schedule, or
implement mitigation measures like masking requirements or air
filters.\comment[id=HM]{cite
\url{https://science.sciencemag.org/content/early/2021/04/28/science.abh2939}} Curfews
may reduce the number of contacts in non-work/non-school settings. In any setting,
measures like masking requirements would reduce the probability of infection associated
with a contact.

@@

Susceptibility to contracting the SARS-CoV-2 virus is dependent on age; so is the
progression of a possible infection. We differentiate between an initial period of
infection without being infectious or showing symptoms, being infectious (presymptomatic
or asymptomatic), showing symptoms, requiring intensive care, and recovery or death. The
probabilities of transitioning between these states depend on age; their duration is
random within intervals calibrated to medical literature (for a detailed description see
Section~\ref{sec:medical_params}. Conditional on the type of contact, infectiousness  is
independent of ages.\comment[id=HM]{Cite current Drosten paper}

The model includes several other features, which are crucial to describe the evolution of
the pandemic in 2020-2021. New virus strains with different profiles regarding
infectiousness and disease progress can be introduced. With a probability calibrated to
\cite{Hunter2021}, vaccinated agents become immune and they do not transmit the virus
\citep{Petter2021, LevineTiefenbrun2021, Pritchard2021}.% the sources only report reduced viral shedding and reduced risk of infection.
% Lauterbach calculated that taking the risk of infection * reduced infectiousness given
% infection based on theses studies suggest that given exposure the risk that fully
% vaccinated individuals pose is <10% of an unvaccinated person.
While vaccines are rolled out, priority may depend on age and occupation. Agents may
demand two types of tests as described in Figure~\ref{fig:pcr_antigen_tests}. First,
polymerase chain reaction (PCR) tests directly reveal whether an individual is infected
or not. PCR tests require some time to be processed and there are always aggregate
capacity constraints. Second, rapid antigen tests yield immediate results. Specificity
and sensitivity of these tests is set according to data by \cite{Bruemmer2021, Smith2021}
. The sensitivity of the rapid antigen tests depends on the timing of the test relative
to the start of infectiousness.\comment[id=HM]{subsequent PCR tests, quarantine,
work/school}. Demand for rapid tests will depend on policy, e.g., prices, testing
requirements before work, attending school, or visiting restaurants and shops.

Modelling a population of agents according to actual demographic characteristics means
that we can use a wide array of data to identify and estimate the model's many
parameters.\footnote{See section S.X of the supplementary materials for an
overview.}\comment[id=HM]{Need to make a list including symbols, maybe you can fetch the
parameters from the model and then we brainstorm re notation?} Mobility data is used to
model the reductions in work contacts. School and daycare policies are incorporated
directly from official directives. Infection rates by age and geographical region are
estimated to match to officially recorded numbers; so is the prevalence of virus strains.
In order to translate simulated cases in our model to officially recorded cases, we use
the model depicted in Figure~\ref{fig:model_for_official_cases}. \comment[id=HM]{Add a
sentence.} A further advantage is that the simulated data have a structure that resembles
datasets used for regression models, which allows additional plausibility checks by
re-running the same models on the model-generated data.\comment[id=HM]{Only keep if we
actually do something like that.}

@@

We apply this model to Germany. In March and April 2020, the country broke the first wave
of the pandemic fairly quickly. Between mid-May and mid-September, daily new infections
were below 20 per Million and day.\comment[id=HM]{Cite our world in data} We model the
period mid-September 2020 to the end of May 2020. We pick the starting date for two
reasons. First, we do not include the first wave because the environment was very
different (e.g., aggregate PCR test capacity was much lower and we would require a very
different model for calculating the share of known cases) and some data was not recorded
yet.\comment[id=HM]{True?}\comment[id=Klara]{ We would definitely need to model national
and international travel which you mention below. Datawise I think everything would be
available. The low numbers during summer in our sample size might also be a problem
because Covid might go extinct in our model when case numbers are so low. } Second,
a large fraction cases during summer of 2020 were traced to international
travel,\comment[id=HM]{citation?}\comment[id=Klara]{There was a comment by minister Spahn
that half of cases during the summer months were due to travel to the Baltic
(\url{https://twitter.com/krstorevic/status/1396516025181556737}) but I know of no data.
We should probably check the RKI reports of July, Aug and Sep} but the precise number is
difficult to model.}

@@

        \includegraphics[width=\textwidth]{../figures/results/figures/data/testing/rapid_test_demand_shares}

        \textcolor{red}{Number of PCR tests}\comment[id=K]{I think this is not available.
        Only a subsection of laboratories report negative PCR tests if I remember right}

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/school_scenarios/full_new_known_case}
        \caption{{\small Recorded Cases: Different schooling scenarios after Easter}}
        \label{fig:schooling_scenarios_easter_new_known_case}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/school_scenarios/full_newly_infected}
        \caption{{\small Total Cases: Different schooling scenarios after Easter}}
        \label{fig:schooling_scenarios_easter_newly_infected}
    \end{subfigure}
    \vskip3ex
